### 2015-04-10 proofs.tex
complete intersection

>>>>

We note that we can write the $B_a$ as polynomials in $c$ with coefficients from the polynomial ring $\mathbb{F}_p[x_i]$. Recall that $B_a$ is the coefficient of $z^p$ in $\left(\sum_{k=0}^\infty x_a^kz^k\right)\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$. Then as polynomials it is clear that $c \mid \binom{c}{k}$ for all $k > 0$; therefore when trying to find the constant term of the coefficient of $z^p$, we can ignore the terms with $k > 0$ in the second multiplicand. The term for $k=0$ is just $1$; it is then clear that the constant term (the coefficient of $c^0$) of the coefficient of $z^p$ is $x_a^p$.

If $\sum_{a=0}^{n-2} \lambda_aB_a=0$ for some $\lambda_a$ rational functions in $c$, we can multiply through by a least common denominator and assume the $\lambda_a$ are polynomials in $c$. Then the constant term of this sum is $\sum_{a=0}^{n-2} C(\lambda_a)x_a^p$ where $C(\lambda_a)$ represents the constant term of $\lambda_a$. Since the $x_a^p$ for $a=0,\dots,n-2$ are clearly linearly independent, we see that $C(\lambda_a)$ must be $0$ for $a=0,\dots,n-2$. Then we can factor out $c$ from all of the $\lambda_a$, since if $\sum_{a=0}^{n-2} \lambda_aB_a=0$, we have $\sum_{a=0}^{n-2}\frac{1}{c}\lambda_aB_a=0$ as well. We can then apply the same logic again to see that the coefficient of $c$ in all of the $\lambda_a$ is $0$. If $e=\max_a\deg \lambda_a$, we need only apply this logic $e$ times to show that the coefficients of $e=1,c,\dots,c^e$ in all of the $\lambda_a$ are $0$, meaning all of the $\lambda_a$ are $0$.

Therefore $B_a$ for $a=0,\dots,n-2$ are linearly independent, and $B_{n-1}=-\sum_{a=0}^{n-2} B_a$. 
Then we need only consider $B_a$ for $a=0,\dots,n-2$, since $B_{n-1}$ is linearly dependent on the others. We will show these generate a complete intersection. Let $I$ be the ideal generated by $B_a$ for $a=0,\dots,n-2$. We see that if $J$ is the kernel of the $\beta$ form, then the since the $B_a$ are killed by the Dunkl operators, we have $I \subseteq J$.

We write $x$ for the vector $\langle x_0,\dots, x_{n-2} \rangle$, where the $x_i$ are taken from the rational function field in $c$ over $\mathbb{F}_p$. Then we can consider $B_a$ as a function on these vectors $x$ for all $a$. For any rational function $u( c)$, we let $u(c )x=\langle u(c )x_0,\dots, u(c )x_{n-2}\rangle$.

To show that $A/I$ is a complete intersection (where $A=k[x_0,\dots,x_{n-2}]$, we will show that if $B_a(x)=0$ for $a=0,\dots,n-2$, then $x=0$.

We showed that for all $a$, $B_a$ is a homogeneous polynomial in the $x_i$ of degree $p$. Then for any rational function $u(c )$, we see that $B_a(u(c )x)=u(c )^pB_a(x)$. In particular, if $B_a(x)=0$, then for any rational function $u(c )$ we have $B_a(u(c )x)=0$ as well. Therefore if $B_a(x) = 0$ for all $a=0,\dots,n-2$, then by choosing a particular polynomial $v(c )$ such that $v(c )x_i$ is a polynomial for all $i=0,\dots,n-2$ (a least common denominator), we see that since $B_a(v(c )x)=0$ that we can just assume the $x_i$ are polynomials in $c$.

For any $a$, we can then consider $B_a(x)$ to be a polynomial in $c$. Since this is zero, we can in particular consider the constant term, which must be $0$. Recall that the constant term of the coefficient of $z^p$ is the constant term of $x_a^p$; this must be the constant term of $x_a$ raised to the $p$ power. If this is zero, then the constant term of $x_a$ must be $0$.

Then if $B_a(x) =0$ for $a=0,\dots,n-2$, we see that the constant terms in all the $x_a$ are $0$. Since the $x_a$ are polynomials in $c$, we can divide through by $c$ again (since $B_a(x)=0$ means $B_a(1/c\cdot x)=0$) and apply the same logic to show that the coefficient of $c$ in all of the $x_a$ must be $0$. Let $d=\max_a \deg x_a$. Then we can just apply this logic $d$ times to show that the coefficients of $1,c,\dots,c^d$ in all of the $x_a$ must be $0$, meaning all of the $x_a$ are $0$ as desired.

Therefore $B_0(x) = \dots = B_{n-2}(x)=0$ implies $x=0$, so $A/I$ is a complete intersection; it then must have Hilbet polynomial $h_{A/I}(t)=(t^p+t^{p-1}+\dots+t+1)^{n-1}$.

By Proposition 3.4 in http://arxiv.org/abs/1107.0504, we see that the Hilbert polynomial of $A/J$ is $(t^p+t^{p-1}+\dots+t+1)^{n-1}h(t^p)$ for some polynomial $h$ with nonnegative integer coefficients; since $I \subseteq J$, we see that $h_{A/I}(t) \ge h_{A/J}(t)$ coefficientwise; however by this restriction of the form of $h_{A/J}(t)$, we see that the only possible choice for $h$ is $h(t)=1$. Therefore $h_{A/I}(t)=h_{A/J}(t)$, so $I=J$ and these $n-1$ generators generate the whole ideal.
